---
title: "README.Rmd"
author: "Uzziel Valencia"
date: "5/3/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Brief Introduction

\n

### Welcome the Binomial Package!

This is a minor package that will help you to do all matter of computation with *binomial probabilities*.


The main functions in this package are the following:

* **bin_choose( )**: Giving the number of successes in a given number of trials
* **bin_probability( )**: Computing the binomial probability under specified conditions
* **bin_distribution( )**: Gives a dataframe with the listed successes and their probabilities
* **bin_cumulative( )**: Gives a dataframe with the listed successes, thier probabilities, and a cumulative count of probabilities
* **bin_variable( )**: Returns a list of all the relevant variables of a binomial distribution

### How to Install

In order to install the package, you will need to use the **devtools** package.

```r
install.packages("devtools") 
```

Then you can install this package from github:

```r
devtools::install_github("stat133-sp19/hw-stat133-UzzielV/tree/master/binomial")
```

If you want to see the fancy-shmancy vignette I built too, you can run the following code:

```r
devtools::install_github("stat133-sp19/hw-stat133-UzzielV/tree/master/binomial", build_vignettes = TRUE)
```

### Now, let's use it!

Running **bin_choose( )**:

```{r}
library(binomial)
bin_choose( n = 5, k = 2)
```

Running **bin_probability( )**:

```{r}
bin_probability(k = 2, n = 5, p = 0.5)
```

Getting a distribution in a data.frame **bin_probability( )**:

```{r}
bin1 <- bin_distribution(n = 5, p = 0.5)
bin1
```

Plotting that distribution **plot( )**:

```{r}
plot(bin1)
```

Getting cumulative frequencies **bin_cumulative( )**:

```{r}
bin_cumulative( n = 5, p = 0.5)
```

Inspecting our variables  **bin_variable( )**:

```{r}
bin_variable(n = 5, p = 0.5)
```

Summarizing the parameters of our binomial variables:

```{r}
bin1 <- bin_variable( n = 10, p = 0.3)
binsum <- summary(bin1)
binsum
```
