---
title: "Intoduction to Binomial Package"
author: "Uzziel Valencia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#>")
library(binomial)

#shift+command+B
```

## Binomial

Welcome to the Binomial package. This **R** package will help you to compute any and all of the most essential binomial funcions.
\n

### Operations
The operations in this package include the following:

* **bin_choose( )**: Giving the number of successes in a given number of trials
* **bin_probability( )**: Computing the binomial probability under specified conditions
* **bin_distribution( )**: Gives a dataframe with the listed successes and their probabilities
* **bin_cumulative( )**: Gives a dataframe with the listed successes, thier probabilities, and a cumulative count of probabilities
* **bin_variable( )**: Returns a list of all the relevant variables of a binomial distribution
\n

#### Summary Operations
There are other functions that give measures of your binomial distribution. Ther are as follows:

* **bin_mean( )** : Gives the expected mean of a distribution that you specify
* **bin_varience( )** : Gives the variance of a distribution that you specify
* **bin_mode( )** : Gives the mode of a distribution that you specify
* **bin_skewness( )** : Gives the skewness of a distribution that you specify
* **bin_kurtosis( )** : Gives the kurtosis (taildness) of a distribution that you specify

\n


### Examples

Let's look at the first aspect of the binomial function, *selection*. In order to run our 'n' *choose* 'k' operation, we simply utilize **bin_choose( )** and specifiy an 'n' and a 'k'.

```{r}
bin_choose( n = 5, k = 2)
```

Neat! Now we've done the first step to computing a binomial distribution.

Let's look at the second step, calling **bin_probability( )**; simply call **bin_probability( )** and fill it with your parameters.

```{r}
bin_probability(k = 2, n = 5, p = 0.5)
```


Wow! Look at the result! The function **bin_probability( )** returns the probability of getting *k* successes in *n* number of trials with the *p* probability of success.
\n

Now in order to get results vizualized, let's use the function **bin_distribution( )** to get a data.frame of our frequencies and their successes.

```{r}
bin1 <- bin_distribution(n = 5, p = 0.5)
bin1
```
Awesome! Now you can see the results of your distribution in a clear table, but what if you want something nicer to look at?
\n
Well, we can plot the information in this dataframe to give our audience something more appealing. This process is relativeley simple with the **plot( )** function.

```{r}
plot(bin1)
```

Nice! How cool is that!? Of course, you can get fancier with the plots on your own time.


\n

Now, what if we want a data.frame with the cumulative probabilities of our distribution? Easy, let's use the function **bin_cumulative ( )** which takes 'n' and 'p'. 

```{r}
#bin_cumulative( n = 5, p = 0.5)
```

Look at that! A data.frame with the cumulative probabilities.

\n

To get back to basics, and just look at the main parameters we're working with, use **bin_variable( )** and get this information in a neat list.

```{r}
bin_variable(n = 5, p = 0.5)
```

Now, let's say you want to get some summary information about your distributions. There is a convenient way to get all this information in one place:

* First call **bin_variable( )** using your trials and probability
* Second call **summary** on your **bin_variable( )** and assign that to a new variable (i.e. 'binsum')
* Third call your new variable

```{r}
bin1 <- bin_variable( n = 10, p = 0.3)
binsum <- summary(bin1)
binsum
```

And now you have all the summary statistics about your distribiution in one specified place!

\n

### Measures

The package Binomial has a number of different tools to get the measures of our binomial probabilities.
\n

To get the mean of our distribution, call **bin_mean( )**.

```{r}
bin_mean( n = 10, p = 0.3)
```

To get the variance of our distribution, call **bin_variance( )**.

```{r}
bin_variance(n = 10, p = 0.3)
```

To get the mode of our distribution, call **bin_mode( )**.

```{r}
bin_mode( n = 10, p = 0.3)
```

To get the skewness of our distribution, call **bin_skewness( )**.

```{r}
bin_skewness( n = 10, p = 0.3)
```

To get the kurtosis (tailed-ness) of our distribution, call **bin_kurtosis( )**.

```{r}
bin_kurtosis( n = 10, p = 0.3)
```
